Inference in Hidden Markov Models with Explicit State Duration Distributions

### 2011-11-02 tex/introduction.tex
a little more nudging of the introduction text

Our contribution is the development of a procedure for EDHMM inference that does not require any hard pre-specification of duration intervals and, as a result, is no longer approximate.  The technique we use to do this 
is borrowed from sampling procedures developed for nonparametric  Bayesian HMM variants \cite{vanGael2008}.  Our key insight is simple: the machinery developed for inference in HMMs with a countable number of states is precisely the same as that which is needed for doing inference in an EDHMM with duration distributions over countable support.  So, while the EDHMM is a distinctly parametric model, the tools from nonparametric Bayesian inference can be applied such that black-box inference becomes possible and, in practice, efficient.

In this work we show specifically that a ``beam-sampling'' approach  \cite{vanGael2008} works for non-approximate estimation of EDHMMs, learning both the transition structure and duration distributions simultaneously.

In demonstrating our EDHMM inference technique we consider a synthetic system  in which the state-cardinality is known and finite, but where each state's duration distribution is unknown. We show that the EDHMM beam sampler performs accurate tracking whilst capturing the duration distributions as well as the probability of transitioning between states.

>>>>

Our contribution is the development of a procedure for EDHMM inference that does not require any hard pre-specification of duration intervals, is efficient in practice, and, as it is an asymptotically exact procedure, does not risk incorrect inference.  The technique we use to do this 
is borrowed from sampling procedures developed for nonparametric  Bayesian HMM variants \cite{vanGael2008}.  Our key insight is simple: the machinery developed for inference in HMMs with a countable number of states is precisely the same as that which is needed for doing inference in an EDHMM with duration distributions over countable support.  So, while the EDHMM is a distinctly parametric model, the tools from nonparametric Bayesian inference can be applied such that black-box inference becomes possible and, in practice, efficient.

In this work we show specifically that a ``beam-sampling'' approach  \cite{vanGael2008} works for  estimating EDHMMs, learning both the transition structure and duration distributions simultaneously.  In demonstrating our EDHMM inference technique we consider a synthetic system  in which the state-cardinality is known and finite, but where each state's duration distribution is unknown. We show that the EDHMM beam sampler performs accurate tracking whilst capturing the duration distributions as well as the probability of transitioning between states.
